Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-17 large_number_squeezing_with_atoms.tex
Minor changes to Josephson paragraph.

The reduction of Eq.~\eqref{eqTwoModeHamiltonian} to the Josephson Hamiltonian has led to the common misconception that no squeezing can be generated in this system if $\chi_+ = 0$ as the effects of the $\Delta\omega$ term are usually dismissed as an irrelevant detuning.  This is not true in general for initial states other than a total number Fock state as the $\Delta\omega(\hat{N})\hat{J}_z$ term leads to a number-dependent detuning.  We demonstrate in this paper that for the case of an initial coherent state this term leads to squeezing.  A spin-echo pulse applied half-way through the experiment which exchanges the population of modes $\ket{a}$ and $\ket{b}$ (which is the protocol used in most spin squeezing experiments) also cancels the effects of this term, and in this case squeezing is only generated if $\chi_+ \neq 0$.  In this work we directly solve Eq.~\eqref{eqTwoModeHamiltonian} demonstrating that squeezing is generated (without a spin-echo pulse) even if $\chi_+=0$.
% We discuss the effects of a spin-echo pulse in Section~\ref{sec:pipulse}

>>>>

The reduction of Eq.~\eqref{eqTwoModeHamiltonian} to the Josephson Hamiltonian has led to the common misconception that no squeezing can be generated in this system if $\chi_+ = 0$ as the effects of the $\Delta\omega$ term are usually dismissed as an irrelevant detuning.  This is not true in general for initial states other than a total number Fock state as the $\Delta\omega(\hat{N})\hat{J}_z$ term leads to a number-dependent detuning.  We demonstrate in this paper that for the case of an initial coherent state this term leads to squeezing.  A spin-echo pulse applied half-way through the experiment which exchanges the population of modes $\ket{a}$ and $\ket{b}$ (which is the protocol used in most spin squeezing experiments) also cancels the effects of this term, and in this case squeezing is only generated if $\chi_+ \neq 0$.  In this work we directly solve Eq.~\eqref{eqTwoModeHamiltonian} demonstrating that squeezing is generated (in the absence of a spin-echo pulse) even if $\chi_+=0$.
% We discuss the effects of a spin-echo pulse in Section~\ref{sec:pipulse}
